Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-21 ijar-npb-ms.tex
Fix typos in proofs
Fix typo and small logical gap in Theorems & Proofs.

\begin{theorem}
  \label{thm:n}
  Let $\beta_n$ denote the Beta-Binomial distribution with probability mass function parameterised as:
  \[ p(l \mid y, n, m, s, N) \propto \frac{B(l + ny + s, m - l + n(1-y) + N - s)}{B(ny + s, n(1-y) + N - s)}, \]
  with $y, m, s,$ and $N$ fixed and unknown.  
  Then,
  \[ y(N+m-1)-s-m > 0 \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
  and 
  \[ y(N+m-1)-s-m < 0 \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
\end{theorem}
The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:n}.

These first-order stochastic domination results now gives the exact 
solution for $\lRsys(\cdot)$ and $\uRsys(\cdot)$.  Thus,
%For $\lRsys(\cdot)$, the minimum is achieved at
%$\nktzu$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k < 0$ and is achieved at 
%$\nktzl$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k > 0$.
%Conversely, for $\uRsys(\cdot)$, the maximum is achieved at 
%$\nktzu$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k > 0$ and is achieved at 
%$\nktzl$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k < 0$.
\begin{align}
\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktz\yktz + s^k_t, m_k - l_k + \nktz(1-\yktz) + n_k - s^k_t)}{B(\nktz\yktz + s^k_t, \nktz(1-\yktz) + n_k - s^k_t)}
    \nonumber\\
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktzo\yktzl + s^k_t, m_k - l_k + \nktzo(1-\yktzl) + n_k - s^k_t)}{B(\nktzo\yktzl + s^k_t, \nktzo(1-\yktzl) + n_k - s^k_t)} \label{eq:LwrSysPost}\\
 &\qquad \qquad \mbox{where } \nktzo = \left\{ \begin{aligned}
   \nktzu & \quad\mbox{if}\quad \yktzl(n_k+m_k-1)-s^k_t-m_k < 0 \\
   \nktzl & \quad\mbox{if}\quad \yktzl(n_k+m_k-1)-s^k_t-m_k > 0 \\
 \end{aligned} \right. \nonumber
\end{align}

@@

  Thus,
  \begin{align*}
    \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} &=
      \frac{(l + n \yu) (m - l - 1 + n (1 - \yl) + N - s)}
           {(l + n \yl) (m - l - 1 + n (1 - \yu) + N - s)} \\
    &> 1 \quad\mbox{when}\quad 0 \le \yl < \yu \le 1
  \end{align*}

@@

  Thus,
  \[ \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} =
      \frac{(l + \nu y) (m - l - 1 + \nl (1 - y) + N - s)}
           {(l + \nl y) (m - l - 1 + \nu (1 - y) + N - s)}
  \]

  However, unlike the case for the $y$ parameter in Theorem \ref{thm:y}, neither $\beta_{\nl}$ 
  nor $\beta_{\nu}$ can be guaranteed to dominate for all possible values 
  for the other parameters, so that necessary conditions for
  monotonicity (either increasing or decreasing) must be established.
  We require,
  \[ \frac{(l + \nu y) (m - l - 1 + \nl (1 - y) + N - s)}
          {(l + \nl y) (m - l - 1 + \nu (1 - y) + N - s)}
     >1
  \]
  After extensive routine algebra, this can be conveniently expressed as
  \begin{align*}
    (\nu - \nl)[y (N + m) - s - y] - l (\nu - \nl)>0.
  \end{align*}
  This limit is hardest to satisfy for $l=m$ since $\nu-\nl>0$.
  Thus, for monotonicity to hold for all $l$, we require
  \begin{align*}
    (\nu - \nl)[y (N + m) - s - y] - m (\nu - \nl) &>0 \\
    \implies (\nu - \nl)[y (N + m - 1) - s - y] &>0
  \end{align*}
  Since $\nu-\nl>0$ by definition, we have a monotonically increasing 
  likelihood ratio only when \[ y (N + m - 1) - s - y > 0. \]  Likewise 
  the likelihood ratio is only monotonically decreasing when
  \[ y (N + m - 1) - s - y < 0. \]
  Thus,
  \[ y(N+m-1)-s-m > 0 \implies \beta_{\nu} \ge_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
  and 
  \[ y(N+m-1)-s-m < 0 \implies \beta_{\nu} \le_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
  by \cite[Theorem 1.C.1, p.43]{shaked2007}.
\end{proof}

>>>>

\begin{theorem}
  \label{thm:n}
  Let $\beta_n$ denote the Beta-Binomial distribution with probability mass function parameterised as:
  \[ p(l \mid y, n, m, s, N) \propto \frac{B(l + ny + s, m - l + n(1-y) + N - s)}{B(ny + s, n(1-y) + N - s)}, \]
  with $y, m, s,$ and $N$ fixed and unknown.  
  Then,
  \[ y > \frac{s + m}{N + m - 1} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
  and 
  \[ y < \frac{s}{N + m - 1} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
  If $\frac{s}{N + m - 1} < y < \frac{s + m}{N + m - 1}$ then first-order stochastic dominance is not guaranteed.
\end{theorem}
The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:n}.

These first-order stochastic domination results now gives the exact 
solution for $\lRsys(\cdot)$ and $\uRsys(\cdot)$.  Thus,
%For $\lRsys(\cdot)$, the minimum is achieved at
%$\nktzu$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k < 0$ and is achieved at 
%$\nktzl$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k > 0$.
%Conversely, for $\uRsys(\cdot)$, the maximum is achieved at 
%$\nktzu$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k > 0$ and is achieved at 
%$\nktzl$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k < 0$.
\begin{align}
\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktz\yktz + s^k_t, m_k - l_k + \nktz(1-\yktz) + n_k - s^k_t)}{B(\nktz\yktz + s^k_t, \nktz(1-\yktz) + n_k - s^k_t)}
    \nonumber\\
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktzo\yktzl + s^k_t, m_k - l_k + \nktzo(1-\yktzl) + n_k - s^k_t)}{B(\nktzo\yktzl + s^k_t, \nktzo(1-\yktzl) + n_k - s^k_t)} \label{eq:LwrSysPost}\\
 &\qquad \qquad \mbox{where } \nktzo = \left\{ \begin{aligned}
   \nktzu & \quad\mbox{if}\quad \yktzl < \frac{s}{N + m - 1} \\
   \nktzl & \quad\mbox{if}\quad \yktzl > \frac{s + m}{N + m - 1} \\
   \mathrm{optimised} & \quad\mbox{if}\quad \frac{s}{N + m - 1} < \yktzl < \frac{s + m}{N + m - 1}
 \end{aligned} \right. \nonumber
\end{align}

@@

  Thus,
  \begin{align*}
    \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} &=
      \frac{(l + n \yu + s) (m - l - 1 + n (1 - \yl) + N - s)}
           {(l + n \yl + s) (m - l - 1 + n (1 - \yu) + N - s)} \\
    &> 1 \quad\mbox{when}\quad 0 \le \yl < \yu \le 1
  \end{align*}

@@

  Thus,
  \[ \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} =
      \frac{(l + \nu y + s) (m - l - 1 + \nl (1 - y) + N - s)}
           {(l + \nl y + s) (m - l - 1 + \nu (1 - y) + N - s)}
  \]

  However, unlike the case for the $y$ parameter in Theorem \ref{thm:y}, neither $\beta_{\nl}$ 
  nor $\beta_{\nu}$ can be guaranteed to dominate for all possible values 
  for the other parameters, so that necessary conditions for
  monotonicity (either increasing or decreasing) must be established.
  We require,
  \[ \frac{(l + \nu y) (m - l - 1 + \nl (1 - y) + N - s)}
          {(l + \nl y) (m - l - 1 + \nu (1 - y) + N - s)}
     >1
  \]
  After extensive routine algebra, this can be conveniently expressed as
  \begin{align*}
    (\nu - \nl)[y (N + m - 1) - s] - l (\nu - \nl)>0.
  \end{align*}
  This limit is hardest to satisfy for $l=m$ since $\nu-\nl>0$.
  Thus, for monotonicity to hold for all $l$, we require
  \begin{align*}
    (\nu - \nl)[y (N + m - 1) - s] - m (\nu - \nl) &>0 \\
    \implies (\nu - \nl)[y (N + m - 1) - s - m] &>0
  \end{align*}
  Since $\nu-\nl>0$ by definition, we have a monotonically increasing 
  likelihood ratio only when \[ y (N + m - 1) - s - m > 0. \]
  By a similar argument, the likelihood ratio is only monotonically decreasing when
  \[ y (N + m - 1) - s < 0. \]
  Thus,
  \[ y > \frac{s + m}{N + m - 1} \implies \beta_{\nu} \ge_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
  and 
  \[ y < \frac{s}{N + m - 1} \implies \beta_{\nu} \le_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
  by \cite[Theorem 1.C.1, p.43]{shaked2007}.  In the intermediate case,
  \[ \frac{s}{N+m-1} < y < \frac{s+m}{N+m-1} \]
  we cannot definitively state the stochastic ordering on $\beta_{\nu}$ and $\beta_{\nl}$.
\end{proof}
